### 2018-04-06 reports/thesis/chapters/5_inference.tex
Added qq plot in inference chapter.

\begin{figure}
    \centering
    \includegraphics[width=0.7\textwidth]{../figures/inference/sig_pixels.eps}
    \caption{Signficiant pixels highlighted at the $z_\alpha = 2$ significance level.}
    \label{fig:sig_pixels}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.7\textwidth]{../figures/inference/z_histo.eps}
    \caption{Histogram of the $z$ statistics}
    \label{fig:z_histo}
\end{figure}

@@

>>>>

\begin{figure}
    \centering
    \includegraphics[width=0.7\textwidth]{../figures/inference/sig_pixels.eps}
    \caption{Significant pixels highlighted at the $z_\alpha = 2$ significance level.}
    \label{fig:sig_pixels}
\end{figure}

\begin{figure}
    \centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
    	\includegraphics[width=\textwidth]{../figures/inference/z_histo.eps}
    \end{subfigure}
	\begin{subfigure}[b]{0.49\textwidth}
    	\includegraphics[width=\textwidth]{../figures/inference/z_qq.eps}
    \end{subfigure}
	}
    \caption{Histogram of the $z$ statistics}
    \label{fig:z_histo}
\end{figure}

@@

The empirical null filter is an extension to the empirical null. In this setting, the parameters of the empirical null varies spatially. Let $Z_{x,y}$ be the test statistic at position $(x,y)$, then
\begin{equation}
	Z_{x,y}\sim\normal\left(
		\mu_{0,x,y},\sigma_{0,x,y}^2
	\right)
\end{equation}
where $\mu_{0,x,y}$ and $\sigma_{0,x,y}$ are the empirical null mean and standard deviation at position $(x,y)$ respectively. The empirical null filter aims to estimate these parameters.

The method is the following. A window size needs to be specified, say $201\times201$. The window is placed over and centred at pixel $(x,y)$ capturing the pixels $z_{i,j}$ for $x-100\leqslant i \leqslant x+100$ and $y-100\leqslant j \leqslant y+100$. The estimators $\widehat{\mu}_{0,x,y}$ and $\widehat{\sigma}_{0,x,y}$ are the empirical null mean and standard deviation estimators, respectively, using the pixels captured in that window. This is then repeated for all $x$ and $y$. The $z$ statistics are then corrected using
\begin{equation}
	\zeta_{x,y} = 
	\dfrac{
		z_{x,y}-\widehat{\mu}_{0,x,y}
	}
	{
		\widehat{\sigma}_{0,x,y}
	}
\end{equation}
and only the corrected test statistics are used in the BH procedure.

There are ways to speed up the implementation of the empirical null filter by sacrificing accuracy. For example, instead of estimating the empirical null parameters for every pixel, a number of them can be estimated and then the remaining values can be interpolated. However it was found that interpolating $\widehat{\sigma}_{0,x,y}$ can yield highly varying results. To avoid this problem, it can be assumed that $\sigma_{0,x,y}=\sigma_0$ for all $x$ and $y$. Then the estimator $\widehat{\sigma}_0$ is the empirical null standard deviation estimator using all location corrected $z$ test statistics.
